Hrvatska u kontekstu europskih konvergencijskih klubova

### 2024-08-28 Paper.Rmd
los

# Print the Robinson test results
print(robinson_results)

@@

```{r fracr2 ,  echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=10, fig.height=6}

# GPH estimator
gph_test_results <- function(data, group_name) {
  result <- fracdiff::fdGPH(data$diff_log_gdp_per_capita)
  #tibble(
  #  group_name = group_name,
  #  gph_d = result$d
  #)
}

@@

# Print the GPH test results
print(gph_results)

@@

```{r fracr3 ,  echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=10, fig.height=6}
# Define the P-GPH estimator function
pgph_test_results <- function(data, group_name) {
  # Run the Phillips-Perron test (as a proxy for P-GPH)
  result <- ur.pp(data$diff_log_gdp_per_capita, type = "Z-alpha", model = "trend")

@@

# Print the P-GPH test results
print(pgph_results)

>>>>

# Print the Robinson test results
kable(
  robinson_results, 
  caption = "Robinson Estimator Results for Income Convergence",
  col.names = c("Group Name", "Robinson d", "P-value"),
  digits = 4,
  align = 'c'
) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>%
add_header_above(c(" " = 1, "Estimation Results" = 2)) # Adds a header above the columns

@@

```{r fracr2 ,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=10, fig.height=6}

# GPH estimator
gph_test_results <- function(data, group_name) {
  result <- fracdiff::fdGPH(data$diff_log_gdp_per_capita)

  # Return a tibble with group name and estimated d value
  tibble(
    group_name = group_name,
    gph_d = result$d
  )
}

@@

# Print the GPH test results
kable(
  gph_results, 
  caption = "GPH Estimator Results for Income Convergence",
  col.names = c("Group Name", "GPH d"),
  digits = 4,
  align = 'c'
) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>%
add_header_above(c(" " = 1, "Estimation Results" = 1))  # Adds a header above the columns

@@

```{r fracr3 ,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=10, fig.height=6}
# Define the P-GPH estimator function
pgph_test_results <- function(data, group_name) {
  # Run the Phillips-Perron test (as a proxy for P-GPH)
  result <- ur.pp(data$diff_log_gdp_per_capita, type = "Z-alpha", model = "trend")

@@

# Print the P-GPH test results

kable(
  pgph_results, 
  caption = "P-GPH Test Results for Income Convergence",
  col.names = c("Group Name", "P-GPH Statistic", "Critical 1%", "Critical 5%", "Critical 10%"),
  digits = 4,
  align = 'c'
) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>%
add_header_above(c(" " = 1, "Estimation Results" = 4))  # Adds a header above the columns
